Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-24 doc/paper.Rmd

library(plotROC)
errorsCV <- rbind(errorrate(cvcs2, 0.001), 
                errorrate(cvcs2, 0.005), 
                errorrate(cvcs2, 0.01), 
                errorrate(cvcs2, 0.05))
errorsCV$method <- "CS2"

@@

cvcs2 %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv))) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(wv~method, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")

>>>>

if (!file.exists("../data/cvcs1.RDS")) {
files <- dir("../data/crossvalidate-cs1/")
cvcs1 <- data.frame()
for (file in files) {
  tmp <- readRDS(file.path("../data/crossvalidate-cs1/",file))
  cvcs1 <- rbind(cvcs1, tmp)
}
cvcs1$coarse <- cvcs1$coarseness
cvcs1$method <- "CS1"
saveRDS(cvcs1, file = "../data/cvcs1.RDS")
} else cvcs1 <- readRDS("../data/cvcs1.RDS")

cvcs <- rbind(cvcs1, cvcs2)

library(plotROC)
errorsCV2 <- rbind(errorrate(cvcs2, 0.001), 
                errorrate(cvcs2, 0.005), 
                errorrate(cvcs2, 0.01), 
                errorrate(cvcs2, 0.05))
errorsCV2$method <- "CS2"

errorsCV1 <- rbind(errorrate(cvcs1, 0.001), 
                errorrate(cvcs1, 0.005), 
                errorrate(cvcs1, 0.01), 
                errorrate(cvcs1, 0.05))
errorsCV1$method <- "CS1"

errorsCV <- rbind(errorsCV1, errorsCV2)

@@

cvcs %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv), linetype=method)) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~wv, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)")
